Country-Level Impact of Education on Entrepreneurship

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

We expect to observe the following causal chain :

@@

>>>>

Drawing from the literature, we expect to observe the following causal chain :

@@

The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, which should be controled for. Which we will do by looking into average perceived entrepreneurial capabilities and fear of failure

indeed an effective explanatory variable, we will need to control for the entrepreneurial self-efficacy
